Data preparation for employee category analysis

### 2023-05-04 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Updating Teleworker rule-based category to Routine teleworker based on HR documentation and then reorders the rule-based categories.

1.  **All remote** - A policy definition for staff that are 100% remote
2.  **Teleworker** - A policy definition for staff that require two days
    per pay period onsite.
3.  **Onsite Flexible** - Defined by `position_category_description` in
    the roster data
4.  **Offsite** - Defined by `position_category_description` in the
    roster data
5.  **Onsite Required** - Defined by `position_category_description` in
    the roster data
6.  **Primarily remote** - Employees who work remotely above the 95th
    percentile <!-- could be 75th -->
7.  **Mostly remote** - Employees who work remotely between the median
    and the 95th percentile <!-- could be 75th -->
8.  **Mostly onsite** - Employees who work remotely between 5th
    percentile and the median <!-- could be 25th -->
9.  **Primarily onsite** - Employees who work remotely below the 5th
    percentile <!-- could be 75th -->

@@

```{r}
prep_building <- 
  prep_building %>% 
  left_join(prep_xx)
```
### Teleworker

Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
```{r}
prep_c <- 
  prep_b %>% 
  left_join(prep_a) %>% 
  fill(period_number, .direction = "down")
```

@@

```{r}
prep_a <- 
  cohort_first %>% 
  select(person_id,position_category_description) %>% 
  character_to_indicator(in_unique_identifier = person_id,
                         position_category_description,
                         in_prefix = "rules_based_position_category_")
```

>>>>

1.  **All remote** - A policy definition for staff that are 100% remote
2.  **Routine teleworker** - Employees with position_category_description's *Onsite Flexible* or *Offsite* that work at least two two days per pay period onsite.
    per pay period onsite.
3.  **Onsite Flexible** - Defined by `position_category_description` in
    the roster data
4.  **Offsite** - Defined by `position_category_description` in the
    roster data
5.  **Onsite Required** - Defined by `position_category_description` in
    the roster data
6.  **Primarily remote** - Employees who work remotely above the 95th
    percentile <!-- could be 75th -->
7.  **Mostly remote** - Employees who work remotely between the median
    and the 95th percentile <!-- could be 75th -->
8.  **Mostly onsite** - Employees who work remotely between 5th
    percentile and the median <!-- could be 25th -->
9.  **Primarily onsite** - Employees who work remotely below the 5th
    percentile <!-- could be 75th -->

@@

@@

```{r, eval=FALSE}
prep_b <- 
  cohort_panel %>% 
  group_by(person_id) %>% 
  summarise(
    across(
      .cols = position_category_description,
      .fns = getmode
    )
  )

prep_c <- 
  cohort_first %>% 
  select(person_id,position_category_description)

prep_c %>% 
  inner_join(prep_a, by = "person_id") %>% 
  filter(position_category_description.x != position_category_description.y)
```

Identify the `position_category_description` at the beginning of the observation window and convert the categories into indicators.

```{r}
prep_xx <- 
  cohort_first %>% 
  select(person_id,position_category_description) %>% 
  character_to_indicator(in_unique_identifier = "person_id",
                         position_category_description,
                         in_prefix = "rules_based_position_category_")
```

### Teleworker

Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.

```{r}
prep_c <- 
  prep_b %>% 
  left_join(prep_a) %>% 
  fill(period_number, .direction = "down")
```

Fourth, take the cohort panel (`cohort_panel`) select `person_id`, `date`, and `daily_status_imputed` and left join to calendar dataframe with filled `period_number` (`prep_c`) on `date`.
